---
title: "Simulating the consequences of unobserved confounding in the CLPM"
author: "Christopher Weber"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Start by simulating some data.

-   Never uses retina figures
-   Has a smaller default figure size
-   Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

```{r}
#devtools::install_github("crweber9874/crossLag")
library(dplyr)
library(crossLag)
simulate_observed_clr(waves = 2, sample.nobs = 2) 
```

The function outputs data for a two wave panel, with 2 observations. Much can be customized, to explore properties of various estimators.

```{r}

invisible(simulate_observed_clr(waves = 2, sample.nobs = 2, 
                      stability.x = 0.5, stability.y = 0.5, 
                      contemporaneous.x = 0.5, cross.x = 0.5, 
                      beta.z = 0.5, beta.u = 0.5, 
                      var.y = 1, var.x = 1, 
                      cov.xy = 0.5, cov.uz = 0.5))
```

The function returns a list, the first element is the lavaan model syntax used to generate the data. The second is the data itself. 

```{r}
library(lavaan)
# Example code to be displayed in the documentation
example_data <- simulate_observed_clr(waves = 3, sample.nobs = 100)
# Fit lavaan model
fit <- sem(example_data$model, data = example_data$data)
summary(fit, fit.measures=TRUE, standardized=TRUE, rsquare=TRUE)
```


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

```         
output:
  rmarkdown::html_vignette:
    fig_caption: yes
```

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
